### 2016-11-04 text/ms.Rmd
Copyediting

\R{A}Superensembles can help address some longstanding
issues in fisheries science.
For example, superensembles assist by not needing to decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could be used to estimate 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or a fisheries selectivity curve parameter.
However, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which superensembles are calibrated.

>>>>

\R{A}Superensembles may be able to assist with some longstanding
issues in fisheries science.
For example, superensembles assist by not needing to decide on one model ---
instead of deciding on dome versus asymptotic fisheries 
selectivity [e.g., @sampson2012], 
or on whether to fix or estimate natural mortality [e.g., @johnson2014],
superensembles can use multiple models to draw inference.
Furthermore, the relative contributions of individual models can help tease apart 
the conditions under which various model assumptions 
result in the most accurate predictions.
Finally, superensembles can be used to directly 
estimate other quantities of interest in fisheries science. 
For instance, superensembles could be used to estimate 
fishing mortality compared to fishing mortality at MSY ($F/F_\mathrm{MSY}$)
or a fisheries selectivity curve parameter.
However, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which they are calibrated.
